\pdftitle

### 2017-05-17 maxNt.tex
intro

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-17T22:51:02+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

% LM: I'd like to avoid common beginnings like "Today blah blah is
% important" or "Blah blah is interesting/fundamental". They feel more like
% a mechanical ritual than a real tentative of connecting with the reader.
This note is mainly addressed to neuroscientists interested in \me\
methods, but its discussion of \enquote{random sampling} formulae may be
useful to all neuroscientists involved in understanding the physical and
dynamical characteristics of brain areas via neuronal recording.

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-17T23:04:18+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

% LM: I'd like to avoid common beginnings like "Today blah blah is
% important" or "Blah blah is interesting/fundamental". They feel more like
% a mechanical ritual than a real tentative of connecting with the reader.
This note is mainly addressed to neuroscientists interested in \me\
methods, but we would be pleased if its discussion of the probability of
\enquote{random sampling} were useful to neuroscientists that use other
statistical methods to study the physical and dynamical characteristics of
brain areas via neuronal recording.
